OpenMPIR

### 2017-09-08 paper.tex
Fixed example figure reference

Compilers implement the majority of their analyses and optimizations on
intermediate representations \textbf{(IRs)} which allow such transformations
to be written once with relative ease and apply to a variety of source front-end
languages such as C or C++.
Historically, the IR of mainstream compilers such as LLVM\cite{llvm} or GCC's Gimple\cite{}
haven't suppored parallel constructs. As a consequence, compilers utilizing these
IRs haven't had the ability to reason about parallelism. The recent work of
Schardl et al.~\cite{tapir} has shown that the LLVM IR can be
extended to represent fork-join parallelism without requiring a major rewrite.
They did so by extending the LLVM instruction set with three instructions
capable of representing fork-join parallelism. To benchmark performance and test
accuracy, they wrote a frontend which translated programs written with Cilk, a parallel
programming model for C/C++, into the Tapir IR. They also implemented a backend to \textbf{lower}
Tapir programs to vanilla LLVM IR with embedded Cilk runtime calls.
They suggested that a similar approach could be taken with OpenMP and other
such frameworks.

@@

To better understand how the OpenMP to Tapir compiler works, we turn to the
\texttt{fib} example from Section~\ref{Sec:OpenMP}. In \figref{fig:Example}
we show what Tapir code is generated.

@@

\caption{Compilation to Tapir}
\label{fig:Example}
\end{figure*}

>>>>

Compilers implement the majority of their analyses and optimizations on
intermediate representations \textbf{(IRs)} which allow such transformations
to be written once with relative ease and apply to a variety of source
front-end languages such as C or C++.  Historically, the IR of mainstream
compilers such as LLVM~\cite{llvm} or GCC's Gimple~\cite{} haven't suppored
parallel constructs. As a consequence, compilers utilizing these IRs haven't
had the ability to reason about parallelism. The recent work of Schardl et
al.~\cite{tapir} has shown that the LLVM IR can be extended to represent
fork-join parallelism without requiring a major rewrite.  They did so by
extending the LLVM instruction set with three instructions capable of
representing fork-join parallelism. To benchmark performance and test accuracy,
they wrote a frontend which translated programs written with Cilk, a parallel
programming model for C/C++, into the Tapir IR. They also implemented a backend
to \textbf{lower} Tapir programs to vanilla LLVM IR with embedded Cilk runtime
calls. They suggested that a similar approach could be taken with OpenMP and
other such frameworks.

@@

To better understand how the OpenMP to Tapir compiler works, we turn to the
\texttt{fib} example from Section~\ref{Sec:OpenMP}. In Figure~\ref{Fig:Example}
we show what Tapir code is generated.

@@

\caption{Compilation to Tapir}
\label{Fig:Example}
\end{figure*}
